\documentclass[]{article}
\begin{document}
  \begin{center}
    \underline{\textbf{Activity report}}
  \end{center}
  \vspace*{20 pt}

First name : Joshua
  \hspace*{120pt}
Last name : PAVIUS GALTIER
  \newline

Date : 2022-10-18
  \hspace*{170pt}
Group : L1\_MI\_ang\_4
  \newline

  Was the activity completed in class or at home? \newline
\indent\emph{It was completed a little bit everywhere}
  \newline
  \indent Other students who participated: \newline
\indent\emph{I was the only one}
  \newline\newline\newline\newline
  Activity type (debate, interview, role play, game, video, etc.):
\indent\emph{I listened to music in english and learnt and understood all the lyrics}
  \newline\newline\newline\newline
  Resources used: Where did you find these resources (CRL, internet, etc.)? Please note all websites used: 
\indent\emph{I listend to music on Spotify or Youtube Music}
  \newline\newline\newline\newline
  Why did you choose this activity? How did it help you accomplish your personal goals?
\indent\emph{Because it's something I often do and I like listening to music while doing something}
  \newline\newline\newline\newline
  How did you prepare for this activity? 
\indent\emph{I opened the app on my phone on my computer}
  \newline\newline\newline\newline
  Feedback: Why was this activity worth your time? Would you recommend it? What might you change next time to make it more successful? 
  \newline\newline
\indent\emph{Yes it was and I would highly recommend it, learning english lyrics is a great way to learn english. And I couldn't think about anything I would change for next time}

\end{document}